\documentclass[12pt, letterpaper]{article}

% Set 1 inch Margins
\usepackage[letterpaper, left=1in, right=1in, top=.6in, bottom=.7in]{geometry}

\setlength{\parindent}{0pt}

% This defines the style for the name/title across the top
\newcommand{\myname}[1]{{\begin{center} \LARGE #1 \end{center} \par }}
% This defines the style for each sub heading (Work, Education, etc..)
\newcommand{\myhead}[1]{{\vspace{2mm} \Large #1 \par}}
% This defines the style for the objective line
\newcommand{\objective}[1]{{\addtolength{\leftskip}{10mm} #1 \par }}
% This defines the style for the company name to be under under work experience
\newcommand{\company}[1]{{\vspace{1mm} \addtolength{\leftskip}{10mm} \textbf{#1} \par}}
% This defines the style for the position title and time 
\newcommand{\position}[2]{{\addtolength{\leftskip}{10mm} \emph{#1} \hfill #2 \par \vspace{1mm}}}
% THis defines the style for the skill used for each position
\newcommand{\skill}[1]{{  \vspace{0.3mm} \addtolength{\leftskip}{20mm} \setlength\parindent{-4mm} $\circ$ #1 \par}}


\begin{document}

\pagestyle{empty}
\raggedright

\myname{Gerald M Nilles}
600 N. Dearborn St. Apt. 1010 \hfill (Home) 847-701-5250 \\
Chicago, IL 60654   \hfill geraldnilles@gmail.com \\
\myhead{Objective}
    \objective{Apply my experience in the competitive smartphone market to develop disruptive technologies in a successful company with massive growth potential.}

\myhead{Work Experience}
    \company{Motorola Mobility}
    \position{Senior Staff Electrical Engineer}{April 2015$-$Present}
    \position{Senior Electrical Engineer}{January 2013$-$April 2015}
        \skill{Designed and validated power architecture for Droid Ultra/Maxx (2013), Droid Turbo (2014), and Moto X Play (2015).}
        \skill{Designed and simulated power delivery network for all critical power rails.}
	\skill{Filed a patent involving intelligent overnight smartphone charging behavior.}
        \skill{Lead cross-functional battery life team and drove down current drain in order to meet marketing goals and maximize battery life satisfaction for end consumers.}
	\skill{Supported mass production by quickly finding the root cause of uncovered issues and identifying short and long term solutions.}
        \skill{Used schematic and PCB CAD tools when designing multilayer PCBs.}

    \company{BlackBerry (formerly Research In Motion)}
    \position{Baseband Design Engineer}{January 2010$-$January 2013}
        \skill{Designed and validated power architecture for BlackBerry Q5 smartphone.}
        \skill{Designed and validated user interface, backlight, and optical sensor circuits for BlackBerry Curve 9360.}

    \company{University of Illinois Power Electronics Laboratory}
    \position{Undergraduate Research Assistant}{March 2009$-$December 2009}
        \skill{Studied, designed and tested various topologies for minimizing current ripple and maximizing efficiency of photovoltaic panels.}
	\skill{Findings published at the Applied Power Electronics Conference and Exposition.}

    \company{Philips Lighting Electronics} 
    \position{Design Engineering Intern, Electronic Fluorescent Lighting}{May 2009$-$August 2009}

    \company{Invensys Appliance Controls}
    \position{Electrical Engineering Intern}{May 2007$-$August 2007}

\myhead{Education}
    \company{University of Illinois at Urbana-Champaign}
    \position{Bachelor of Science in Electrical Engineering}{August 2005$-$December 2009}
        \skill{Major: Electrical Engineering $-$ Minor: Computer Science}
        \skill{Emphasis in power electronics and electric machines}
	\skill{GPA 3.73/4.00}

\begin{center}
\small
References available on request
\end{center}
\end{document}

